Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-10-21 thesis/paper_draft.qmd
minor fixes to algorithm

$$
\hat{\boldsymbol{W}}^{N}_{1} = \lambda_{\delta} \hat{\boldsymbol{W}}_{1, \delta} + (1 - \lambda_{\delta}) \hat{\boldsymbol{W}}_1,
$$ {#eq-novelist-cov}

@@

\For{$i = v:T-1$}
    \State $j = i - v +1$
    \State $\hat{\boldsymbol{W}}_j = \frac{1}{v} \sum_{t=j}^{i} \hat{\boldsymbol{e}}_{t} \hat{\boldsymbol{e}}_{t}'$
    \State $\hat{\boldsymbol{D}}_j = \text{diag}(\hat{\boldsymbol{W}}_j)$
    \State $\hat{\boldsymbol{R}}_j = \hat{\boldsymbol{D}}_j^{-1/2} \hat{\boldsymbol{W}}_j \hat{\boldsymbol{D}}_j^{-1/2}$
    \For{$\delta \in \Delta$}
        \State Compute thresholded correlation $\hat{\boldsymbol{R}}_{j,\delta}$ using Equation 5
        \State Compute $\hat{\lambda}_{j,\delta}$ using Equation 6
        \State Compute $\hat{\boldsymbol{R}}^{N}_{j,\delta}$ using Equation 4
        \State $\hat{\boldsymbol{W}}^{N}_{j,\delta} = \hat{\boldsymbol{D}}_j^{1/2} \hat{\boldsymbol{R}}^{N}_{j,\delta} \hat{\boldsymbol{D}}_j^{1/2}$
        \State $\boldsymbol{G} = (\boldsymbol{S}' \hat{\boldsymbol{W}}^{N^{-1}}_{j,\delta} \boldsymbol{S})^{-1} \boldsymbol{S}' \hat{\boldsymbol{W}}^{N^{-1}}_{j,\delta}$
        \State Reconciled forecasts $\tilde{\boldsymbol{y}}_{i+1 | \delta} = \boldsymbol{S} \boldsymbol{G} \hat{\boldsymbol{y}}_{i+1}$
        \State $\tilde{\boldsymbol{e}}_{i+1 | \delta} = \boldsymbol{y}_{i+1} - \tilde{\boldsymbol{y}}_{i+1 | \delta}$
    \EndFor
\EndFor

\State $\text{MSE}_{\delta} = \frac{1}{T-v} \sum_{i=v}^{T-1} (\tilde{\boldsymbol{e}}_{i+1 | \delta})^2$ for each $\delta \in \Delta$
\State $\hat{\delta}^* = \arg\min_{\delta \in \Delta} \text{MSE}_{\delta}$
\State Compute $\hat{\lambda}^*$ on all training data using $\hat{\delta}^*$
\State Compute $\hat{\boldsymbol{R}}_1^*$ using $\hat{\delta}^*$ and $\hat{\lambda}^*$ on all training data, using Equation 3

\State \textbf{Output:} Estimate of optimal $\hat{\delta}^*$

@@

*Remark.* Minimising a multi-step-ahead forecast error metric in the cross-validation procedure oftern yields a $\hat{\delta}^*$ that is close to the 1-step-ahead case.

>>>>

$$
\hat{\boldsymbol{W}}^{N}_{1} = \lambda_{\delta} \hat{\boldsymbol{W}}_{1, \delta} + (1 - \lambda_{\delta}) \hat{\boldsymbol{W}}_1,
$$

@@

\For{$i = v:T-1$}
    \State $j = i - v +1$
    \State $\hat{\boldsymbol{W}}_j = \frac{1}{v} \sum_{t=j}^{i} \hat{\boldsymbol{e}}_{t} \hat{\boldsymbol{e}}_{t}'$
    \State $\hat{\boldsymbol{D}}_j = \text{diag}(\hat{\boldsymbol{W}}_j)$
    \State $\hat{\boldsymbol{R}}_j = \hat{\boldsymbol{D}}_j^{-1/2} \hat{\boldsymbol{W}}_j \hat{\boldsymbol{D}}_j^{-1/2}$
    \For{$\delta \in \Delta$}
        \State Compute thresholded correlation $\hat{\boldsymbol{R}}_{j,\delta}$ using Equation 2
        \State Compute $\hat{\lambda}_{j,\delta}$ using Equation 3
        \State Compute $\hat{\boldsymbol{R}}^{N}_{j,\delta}$ using Equation 1
        \State $\hat{\boldsymbol{W}}^{N}_{j,\delta} = \hat{\boldsymbol{D}}_j^{1/2} \hat{\boldsymbol{R}}^{N}_{j,\delta} \hat{\boldsymbol{D}}_j^{1/2}$
        \State $\boldsymbol{G} = (\boldsymbol{S}' \hat{\boldsymbol{W}}^{N^{-1}}_{j,\delta} \boldsymbol{S})^{-1} \boldsymbol{S}' \hat{\boldsymbol{W}}^{N^{-1}}_{j,\delta}$
        \State Reconciled forecasts $\tilde{\boldsymbol{y}}_{i+1 | \delta} = \boldsymbol{S} \boldsymbol{G} \hat{\boldsymbol{y}}_{i+1}$
        \State $\tilde{\boldsymbol{e}}_{i+1 | \delta} = \boldsymbol{y}_{i+1} - \tilde{\boldsymbol{y}}_{i+1 | \delta}$
    \EndFor
\EndFor

\State $\text{MSE}_{\delta} = \frac{1}{T-v} \sum_{i=v}^{T-1} (\tilde{\boldsymbol{e}}_{i+1 | \delta})^2$ for each $\delta \in \Delta$
\State $\hat{\delta} = \arg\min_{\delta \in \Delta} \text{MSE}_{\delta}$

\State \textbf{Output:} Estimate of optimal threshold parameter $\hat{\delta}$

@@

*Remark.* Minimising a multi-step-ahead forecast error metric in the cross-validation procedure oftern yields a $\hat{\delta}$ that is close to the 1-step-ahead case.
